How much is too much? Item Response Theory procedures to shorten tests

### 2025-02-24 sis2025/LaTex+Package/styles/paper-sis-template.tex
voglio morire

\color{red}
Non è propriamente così, frank calcola tutte le IIF all'inziio considerando i parametri degli item in $B'$ e se le porta avanti ma quindi dovrei creare un altro oggetto che contiene tutte le iif i? ci provo tanto ormai è tutto una merda 
\normalcolor

@@

The procedure is replicated 100 times. At each replica, a test of $B$ of 50 items with difficulty ($b_i \sim \mathcal{U}(-3, 3)$) discrimination ($a_i \sim \mathcal{U}(.90, 2)$) parameters drawn from uniform distributions is generated. Lucky 
guess and careless error parameters are constant, $c_i = 0, \forall i \in B$ and $d_i = \, \forall i \in B$.
The $\text{TIF}_B$ is obtained as the average TIF  from the items in $B$, and describes the measurement precision that would be obtained if respondents were administered with all the items without getting tired.

A new test $B'$ is generated by keeping the item parameters equal to those in $B$, with the only exception of the careless error parameters, which are included as related to the rank of the item in the item bank with an exponential function. 
The assumption is that the first administered item does not have a careless error probability ($d_{1^{st}} = 1$), but it increases as the administration goes on. As such, the careless error probabilities associated to the second and third administered items are, respectively, $d_{2^{nd}} = .99$ and $d_{3^{rd}}.98$. In this application, the maximum careless error probability associated to the last administered item is $d_{50^{th}} = .61$.

\color{blue}
At each replication, Frank and Léon generate a STF for approximating $\text{TIF}_B$.
%La differenza è che Frank calcola tutte le iif degli tiem all'inizio, consdierando la careless error legata alla posizione dell'item così come viene generata inizialmente dalla funzione. 
%Léon invece calcola la iif ad ogni itereazione (per questo è più lento) mettendo dentro la careless error che è legata alla posizione dell'item. Nel senso, se Léon per ora ha selezionato 3 item e deve valutare se metterne un quarto, le iif degli item che sono rimasti verrà calcolata considerando la careless error in $B'$ dell'item somministrato per quarto.
\normalcolor

@@

The performance of Léon has been compared 
The ability of Frank and Léon in reducing the distance from the $\text{TIF}_B$ has been considered. 
Moreover, the TIF of the items in $B'$ has been computed as well and compared against those of the STFs resulting from the application of Frank and Léon. 
The rationale is as follows. The more the item in a test, the higher the information for different regions of the latent trait. 
However, administering too many items might be an highly demanding task, such that the respondent might get tired and their response accuracy might decrease during the administration, such that the last administered items might include error variance not related to the construct under investigation. 
In this light, it should be more convenient to administer less but highly informative items, able to approximate a specific TIF target, than to administer the entire test to obtain precise measurements of the latent trait.

>>>>

@@

The procedure is replicated 100 times. At each replica, a test of $B$ of 50 items with difficulty ($b_i \sim \mathcal{U}(-3, 3)$) discrimination ($a_i \sim \mathcal{U}(.90, 2)$) parameters drawn from uniform distributions is generated. Lucky 
guess and careless error parameters are constant, $c_i = 0, \forall i \in B$ and $d_i = \, \forall i \in B$.
The $\text{TIF}_B$ (i.e., the TIF-target) is obtained as the average TIF  from the items in $B$, and describes the measurement precision that would be obtained if respondents were administered with all the items without getting tired.

\color{blue}
A new test, $B'$, is generated at each replication, where $b_i' = b_i$, $a_i' = a_i$, $c_i = 0$, $\forall i \in B'$, and $d_i' = \exp(-\lambda r_i)$, with $\lambda = 0.01$ and $r = \{0, \ldots I -1\}$.

At each replication, Frank and Léon generate a STF for approximating the $\text{TIF}_B$. Moreover, the average TIF is computed considering the item with the tiredness effect in $B'$, denoted as $\text{TIF}_{B'}$.
%La differenza è che Frank calcola tutte le iif degli tiem all'inizio, consdierando la careless error legata alla posizione dell'item così come viene generata inizialmente dalla funzione. 
%Léon invece calcola la iif ad ogni itereazione (per questo è più lento) mettendo dentro la careless error che è legata alla posizione dell'item. Nel senso, se Léon per ora ha selezionato 3 item e deve valutare se metterne un quarto, le iif degli item che sono rimasti verrà calcolata considerando la careless error in $B'$ dell'item somministrato per quarto.
\normalcolor

@@

The average distance from $\text{TIF}_B$ of the STFs generated by Frank and Léon at each iteration, as well as of the test obtained from $B'$ has been considered as a criterion for evaluating the ability of Léon of generating informative STFs while accounting for the tiredness of the respondents, $\Delta_x = |\text{TIF}_B - \text{TIF}_{Q_x}|$, with $x \in \{B', \text{Frank}, \text{Léon}\}$.  Trivially, when the $\text{TIF}_\{B'\}$ is considered, $Q = B'$.

To better understand whether acknowledging the tiredness of the respondents influences the number of items included in $Q$, the cardinalities of the STFs generated by Frank and Léon, $||Q_{\text{Frank}}||$ and $||Q_{\text{Léon}}||$, respectively, have been compared.

%Moreover, the TIF of the items in $B'$ has been computed as well and compared against those of the STFs resulting from the application of Frank and Léon. 
%The rationale is as follows. The more the item in a test, the higher the information for different regions of the latent trait. 
%However, administering too many items might be an highly demanding task, such that the respondent might get tired and their response accuracy might decrease during the administration, such that the last administered items might include error variance not related to the construct under investigation. 
%In this light, it should be more convenient to administer less but highly informative items, able to approximate a specific TIF target, than to administer the entire test to obtain precise measurements of the latent trait.
